resistanceModelNotesAndy

### 2016-03-04 paper1_results_figs.Rmd
working on figures

---
## Fig. x2 How time-to-resistance is effected by input values for each insecticide use strategy

@@

## How difference in time-to-resistance between sequential and adaptive mixture is effected by input values

@@

>>>>

## Fig. x2 How time-to-resistance is effected by input values for each insecticide use strategy

@@

## Fig. x3 How difference in time-to-resistance between sequential and adaptive mixture is effected by input values

@@

  #can I do a 2D hexbin plot with x=exposure, y=effectiveness
  #but do I just want to use 1 effectiveness, or maybe add both effectivenesses together ?
  #bin colour : proportion of runs in which sequential better & could have diverging scale about 0.5
  #I probably still need to tweak data first
  #currently I have differences in times to resistance : mixA_minus_seq0.25
  #what I think I want is the proportion of runs in which mix is better
  #I can get that by setting to 0 & 1 and calc average
  # tst_runs <- c(1,0,0,0)
  # tst_runs <- c(1,1,1,0)
  # mean(tst_runs)

  ggSubset <- df_diff
  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_diff <- abs(ggSubset$mixA_minus_seq0.25)

  #takes a long time to plot, initial version gave me count
  #I want it to plot the mean
  #check stackoverflow ..

    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
             geom_hex()
             #points not wanted if 10000
             #geom_point(shape=1, colour="darkblue", alpha=0.2, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             #geom_smooth(linetype='dashed',size=1, colour="red") +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             #labs(title = i) +
             #geom_hline(yintercept = 0, colour="white")
           )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_better_seq0.25))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mixA_better_seq0.25))+

             geom_point(alpha=0.2)  
           )

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mixA0.25))+
             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             theme(legend.position="none") +
             geom_point(alpha=1)  
           )

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_minus_seq0.25))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

             #didn't manage to get the colorBrewer scale to diverge from 0
             #scale_colour_distiller("RdYlGn",type='div')
            )

    #COOLIO !! I really like this figure.
    library(viridis)
    #try facetted showing generation differences, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #?viridis
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             geom_point(alpha=1)  
           )

### 2016-03-04 paper1_results_figs_slimmed.Rmd
working on figures

## Main Figures for paper 1 : version 1 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Exposure has the greatest effect on time-to-resistance.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) adaptive mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer tp reach the resistance threshold, and above this 'mixture switching to sole use' takes longer.

@@

\pagebreak

# Fig. x1 Time-to-resistance across all input values

@@

\pagebreak

# Fig x2 PRCC analysis for time-to-resistance for sequential and mixture strategies

@@

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste(strategy,"time-to-resistance 0.25")) +
             xlab(NULL) 
  }

@@

>>>>

## Main Figures for paper 1 : version 2 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.

@@

\pagebreak
## Fig. x1 Time-to-resistance across all input values

@@

\pagebreak
## Fig x2 PRCC analysis for time-to-resistance 0.25 for sequential and mixture strategies

@@

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             ggtitle(paste(strategy)) +
             xlab(NULL) 
  }

@@

\pagebreak
## Fig. x3 How time-to-resistance is effected by input values for each insecticide use strategy

1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer.

```{r, eval=TRUE, echo=FALSE, fig.height=2.5}

  #names_inputs <- names(ggInsOuts)[1:num_inputs]

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","maleExposureProp")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

  #num_inputs <- length(in_cols)
  #names_inputs <- in_cols

  #to rearrange order of legend entries
  ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential", "Mix either")) #, labels=c("MBB", "MAA", "MCC"))

  #TODO could I facet the plots below rather than using the loop
  #probably need to put all inputs into a single column and then facet by that

  #for(i in names_inputs)
  for(i in in_cols)
    {
    #x11()

    y <- 'time_to_resistance0.25'

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

\pagebreak
## Fig. x4 PRCC difference in time-to-resistance 0.25 between sequential and adaptive mixture strategies

1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

    x <- df_diff[,1:num_inputs]
    y <- df_diff["mixA_minus_seq0.25"]

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             #ggtitle(paste("PRCC difference between sequential and mixture adaptive")) +
             xlab(NULL)
          )

\pagebreak
## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises faster under adaptive mixture or sequential strategies

```{r, eval=TRUE, echo=FALSE, fig.height=5}

  ggSubset <- df_diff
  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_diff <- abs(ggSubset$mixA_minus_seq0.25)

    #COOLIO !! I really like this figure.
    library(viridis)
    #try facetted showing generation differences, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix\nslower to reach resistance',
                                                                        '1'='sequential\nslower to reach resistance'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #?viridis
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in\ngenerations\nto reach\nresistance\nthreshold")) + 
             theme_bw() +
             #theme_minimal() +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') +             
             geom_point(alpha=1, size=0.5)  
           )

### 2016-03-04 resistanceModelNotesAndy.Rmd
working on figures

@@

### TO DO

~ can I facet the PRCC mutliplots so I just get one axis ?

@@

>>>>

** 2/3/2016 **

@@

~ modifying PRCC mutliplots to get just one axis

** 3/3/2016 **

msg from Ian :

Aha! I've understood what he means by setting correct_deploy to 0, to study mosaics.

### TO DO  
~ check stackoverflow for getting mean into hexbin plot

~ communicate my concern to Ian that figures I've spent quite a long time on just go into supplementary material where few will see them. Can we think of a way of getting these into a paper themselves ? e.g. if this first paper is targeted at policy people can we get a 2nd paper that is targetted at biologists and explores mechanisms ?

~ can I change order of strategies in legend ?
~ can I facet the smoothed scatter plots to get them to take up less space and avoid repeating legend ?
~~ or I may be able to use a similar plot_grid() method

~~ if I wanted to facet by inputs might need to restructure the data, put inputs into a single column to replace below :
  for(i in names_inputs)
  {
    print( ggplot(ggSubset, aes_string(x=i

~ Ian wants trees. Maybe just do one tree of resistance0.25 on whether seq or maxAdapt is better.

adaptive & sequential
20% longer

@@

~ I could try a 2D plot with x=exposure, y=effectiveness & hexbin & colour cells according to proportion of runs where mix or seq is better.

~~ seq is sometimes better than mix both. Where does that occur. The above plot might even help to answer that.
